### 2016-07-07 lineups.Rnw
does it still crash? - I'm using dplyr_0.5.0

\begin{figure}
\begin{subfigure}[t]{.45\textwidth}
\caption{Realization of a jumping transitive triplet, where $i$ is the focal actor, $j$ is the target actor, and $h$ is the intermediary. The group of the actors is represented by the shape of the node.}
<<jtt, echo=FALSE, fig.width=2, fig.height=2, message = FALSE, warning = FALSE, fig.align='center'>>=
jTTe <- data.frame(from = c('i', 'i', 'h'), to = c('h', 'j', 'j'))
jTTn <- data.frame(id = letters[8:10], group = c(1,1,2))

@@

\begin{figure}
\centering
<<echo=FALSE, fig.with=8, fig.height = 8, out.width='.6\\linewidth'>>=
load("Data/lus_ests_truth.rda")

@@

# merge in true values:
truth <- unique(subset(lus_ests_truth, true_panel==TRUE)[,c("lineupid", "true_model","param_name","true_value")])
#dim(lus_spread)
lus_spread <- merge(lus_spread, truth, by=c("lineupid","true_model", "param_name"), all.x=TRUE)
lus_spread$true_value[is.na(lus_spread$true_value)] <- 0
#qplot(M2, true_value, facets=~param_name, data=lus_spread, colour=true_model)
#qplot(M3, true_value, facets=~param_name, data=lus_spread, colour=true_model)

@@

lus_summary_2 <- lus_spread %>% dplyr::group_by(part, lineupid, param_name) %>%
  dplyr::summarize(
    data_n = sum(true_model=="M2"),
    data_est = mean(M2[true_model=="M2"]),
    data_sd = sd(M2[true_model=="M2"], na.rm=TRUE),
    null_est = list(M2[true_model=="M1"]),
    data_dist = data_est - max(unlist(null_est))),
  upper_qu = sum(data_est > unlist(null_est)) / (n()-1) )

# XXX The lines commented out above crash my RStudio. I haven't figured out why yet! :( XXX

@@

lus_summary_3 <- lus_spread %>% group_by(part, lineupid, param_name) %>%
  summarize(
    data_n = sum(true_model=="M3"),
    data_est = mean(M3[true_model=="M3"]),
    data_sd = sd(M3[true_model=="M3"], na.rm=TRUE),
    null_est = list(M3[true_model=="M1"]),
    data_dist = min(unlist(null_est)) - data_est,
    lower_qu = sum(data_est < unlist(null_est))/(n()-1)
  )

p2 <- qplot(data_dist, lower_qu,  data = subset(lus_summary_3, !is.na(lower_qu) & param_name=="number pairs at doubly achieved distance 2")) +
  facet_grid(.~part) +
  xlab("Difference in M3 estimate of data panel and minimum of the null panels") +
  ylab("Ratio of null panels with larger M3 estimate") +
  ggtitle("doubly achieved distance")

gridExtra::grid.arrange(p1,p2)
@
\caption{\label{fig:lusparms} Scatterplots }
\end{figure}

>>>>

\begin{figure}
\begin{subfigure}[t]{.45\textwidth}
\caption{\label{fig:jtt}Realization of a jumping transitive triplet, where $i$ is the focal actor, $j$ is the target actor, and $h$ is the intermediary. The group of the actors is represented by the shape of the node.}
<<jtt, echo=FALSE, fig.width=2, fig.height=2, message = FALSE, warning = FALSE, fig.align='center'>>=
jTTe <- data.frame(from = c('i', 'i', 'h'), to = c('h', 'j', 'j'))
jTTn <- data.frame(id = letters[8:10], group = c(1,1,2))

@@

\begin{figure}
\centering
<<echo=FALSE, fig.width=8, fig.height = 8, out.width='.6\\linewidth', warning = FALSE>>=
load("Data/lus_ests_truth.rda")

@@

# merge in true values:
truth <- unique(subset(lus_ests_truth, true_panel==TRUE)[,c("lineupid", "true_model","param_name","true_value")])

lus_spread <- merge(lus_spread, truth, by=c("lineupid","true_model", "param_name"), all.x=TRUE)
lus_spread$true_value[is.na(lus_spread$true_value)] <- 0

@@

lus_summary_2 <- lus_spread %>% dplyr::group_by(part, lineupid, param_name) %>%
  dplyr::summarize(
    data_n = sum(true_model=="M2"),
    data_est = mean(M2[true_model=="M2"]),
    data_sd = sd(M2[true_model=="M2"], na.rm=TRUE),
    data_dist = data_est - max(M2[true_model=="M1"]),
    upper_qu = sum(data_est > M2[true_model=="M1"]) / (n()-1) 
)

@@

lus_summary_2b <- lus_spread %>% dplyr::group_by(part, lineupid, param_name) %>%
  dplyr::summarize(
    data_n = sum(true_model=="M1"),
    data_est = mean(M2[true_model=="M1"]),
    data_sd = sd(M2[true_model=="M1"], na.rm=TRUE),
    data_dist = data_est - min(M2[true_model=="M2"]),
    lower_qu = sum(data_est < M2[true_model=="M2"]) / (n()-1) 
)

p2 <- qplot(data_dist, lower_qu, data = subset(lus_summary_2b, !is.na(data_dist) & param_name=="transitive triplets jumping alcohol2" & part %in% c("smallfriends", "smallfriends-rev"))) +
  facet_grid(.~part) + xlab("Difference in M2 estimate of data panel and minimum of the null panels") +
  ylab("Ratio of null panels with larger M2 estimate") +
  ggtitle("jumping transitive triplets")

gridExtra::grid.arrange(p1,p2)
@
\caption{\label{fig:lusparms} Scatterplots of smallfriends and smallfriends-rev: comparing the ratio of null plots with smaller estimates of $\beta_3$ in the nulls than in the data panel (top row) and larger estimates of $\beta_3$ in the nulls than in the data panel. In lineups with a ratio of 1 the data should be 'easy' to identify in both scenarios.}
\end{figure}

\begin{figure}
\centering
<<echo=FALSE, fig.width=8, fig.height = 8, out.width='.6\\linewidth'>>=
lus_summary_3 <- lus_spread %>% group_by(part, lineupid, param_name) %>%
  summarize(
    data_n = sum(true_model=="M3"),
    data_est = mean(M3[true_model=="M3"]),
    data_sd = sd(M3[true_model=="M3"], na.rm=TRUE),
    data_dist = min(M3[true_model=="M1"]) - data_est,
    lower_qu = sum(data_est < M3[true_model=="M1"])/(n()-1)
  )

p1 <- qplot(data_dist, lower_qu,  data = subset(lus_summary_3, !is.na(lower_qu) & param_name=="number pairs at doubly achieved distance 2")) +
  facet_grid(.~part) +
  xlab("Difference in M3 estimate of data panel and minimum of the null panels") +
  ylab("Ratio of null panels with larger M3 estimate") +
  ggtitle("doubly achieved distance")

#gridExtra::grid.arrange(p1,p2)
p1
@
\caption{\label{fig:lusparms-eff2} }
\end{figure}
